### 2018-04-30 paper/message-passing-design.tex
this compiles

\NewAlgorithm{\Fwd}{Forward}
\NewAlgorithm{\Send}{BuildRouteSender}
\NewAlgorithm{\Recv}{BuildRouteReceiver}
\NewAlgorithm{\ExtendRoute}{ExtendRoute}
\NewAlgorithm{\CreateOnionLayer}{CreateOnionLayer}
\NewAlgorithm{\Dec}{Dec}
\NewAlgorithm{\Store}{Store}
\NewVariable{\sk}{sk}
\NewVariable{\rdv}{rdv}
\NewVariable{\LRV}{\mathcal{L_{RV}}\xspace}
\NewVariable{\Hsend}{\mathcal{H}_{\text{send}}\begin{algorithmic}[1]}
\NewVariable{\Hrec}{\mathcal{H}_{\text{rec}}\begin{algorithmic}[1]}
\NewVariable{\Hforward}{\mathcal{H}_{\text{forward}}\begin{algorithmic}[1]}
\NewVariable{\Hbackward}{\mathcal{H}_{\text{backward}}\begin{algorithmic}[1]}
\NewVariable{\Hsendforward}{\mathcal{H}_{\text{send forward}}\begin{algorithmic}[1]}
\NewVariable{\Hsendbackward}{\mathcal{H}_{\text{send backward}}\begin{algorithmic}[1]}
\NewVariable{\Hrecforward}{\mathcal{H}_{\text{rec forward}}\begin{algorithmic}[1]}
\NewVariable{\Hrecbackward}{\mathcal{H}_{\text{rec backward}}\begin{algorithmic}[1]}

@@

Another difference from Tor, where connections are established by all nodes in the route, \name is stateless: the route's ends (the sender Alice and receiver Bob) cooperate to create the headers containing all the necessary routing information for future communication between Alice and Bob.
In that regard, two headers are required: $\Hforward$ to route packets from Alice to Bob, and $\Hbackward$ for packets from Bob to Alice.

To implement our predictive onion routing mechanism, \name is thus split in two algorithms: the route building one, and the message routing one.
Figure~\ref{fig:file-exchange} shows the process of the route creation until the first exchange of a file chunk from Alice to Bob.
Bob uses the backward route to send acknowledgments back to Alice.

@@

Bob sends \Hrecforward and the descriptors of the \LRV nodes to Alice.
Alice still has her part of the route to create: like Bob, she randomly picks nodes to constitutes $l$ layers from her \squad to \LRV.

@@

\begin{figure}[t]
  %\framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
    % \Require{%
    %   $D$ is the set of alternative recipient devices.
    % }
    \Function{\Recv}{$D$}
      \State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
      \State \Return $H_\rdv$
        \Comment{Give to sender out-of-bound.}
    \EndFunction
  \end{algorithmic}
  %\end{minipage}}

@@

  \vspace{0.3em}
  %\framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
    % \Require{%
    %   $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
    %   \(D\) is a set of device addresses.
    %   $\pk_D$ is the public key of device set $D$.
    %   $L$ is the length of the route,
    %   $\theta$ is the threshold of probability of failure.%
    % }
    \Function{\ExtendRoute}{$H, L, \theta$}
      \If{$L\leq 0$}
        \State \Return $H$
      \EndIf
      \State $D\gets \CreateOnionLayer[\theta]$
      \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
      \State \Return $\ExtendRoute[H, L-1, \theta]$
    \EndFunction
  \vspace{0.3em}
    \Function{\CreateOnionLayer}{$\theta$}
      \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
      \State $D\gets \{(d, \pk_d, p_d)\}$
      \While{$\prod_{d\in D} p_d > \theta$}
        \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
        \State $D\gets D\cup \{(d, \pk_d, p_d)\}$
      \EndWhile
      \State \Return $D$
    \EndFunction
  \end{algorithmic}
  %\end{minipage}}
  \caption{\label{fig:route building algo}The route building algorithm}
\end{figure}

>>>>

\NewAlgorithm{\Fwd}{Forward}
\NewAlgorithm{\Send}{BuildRouteSender}
\NewAlgorithm{\Recv}{BuildRouteReceiver}
\NewAlgorithm{\ExtendRoute}{ExtendRoute}
\NewAlgorithm{\CreateOnionLayer}{CreateLayer}
\NewAlgorithm{\Dec}{Dec}
\NewAlgorithm{\Store}{Store}
\NewVariable{\sk}{sk}
\NewVariable{\rdv}{rdv}
\NewVariable{\LRV}{\mathcal{L_{RV}}\xspace}
\NewVariable{\Hsend}{\mathcal{H}_{\text{send}}\xspace}
\NewVariable{\Hrec}{\mathcal{H}_{\text{rec}}\xspace}
\NewVariable{\Hforward}{\mathcal{H}_{\text{forward}}\xspace}
\NewVariable{\Hbackward}{\mathcal{H}_{\text{backward}}\xspace}
\NewVariable{\Hsendforward}{\mathcal{H}_{\text{send forward}}\xspace}
\NewVariable{\Hsendbackward}{\mathcal{H}_{\text{send backward}}\xspace}
\NewVariable{\Hrecforward}{\mathcal{H}_{\text{rec forward}}\xspace}
\NewVariable{\Hrecbackward}{\mathcal{H}_{\text{rec backward}}\xspace}

@@

Another difference from Tor, where connections are established by all nodes in the route, \name is stateless: the route's ends (the sender Alice and receiver Bob) cooperate to create the headers containing all the necessary routing information for future communication between Alice and Bob.
In that regard, two headers are required: \Hforward to route packets from Alice to Bob, and \Hbackward for packets from Bob to Alice.

To implement our predictive onion routing mechanism, \name is thus split in two algorithms: the route building one, and the message routing one.
Figure~\ref{fig:file-exchange} shows the process of the route creation until the first exchange of a file chunk from Alice to Bob.
Alice uses the forward route to send file chunks to Bob, while Bob uses the backward route to send acknowledgments back to Alice.

@@

Bob sends \Hrecforward and the descriptors of the \LRV nodes to Alice.
Alice still has her part of the route to create: like Bob, she randomly picks nodes to constitutes $l$ layers from her \squad to \LRV.
She also build two headers: \Hsendforward contains the route from her \squad (excluded) to \LRV (included), while \Hsendbackward contains the route from \LRV (excluded) to her \squad (included).
Alice finally sends \Hsendbackward back to Bob: he is going to need it to sends acknowledgments back to Alice.

@@

\begin{figure}[t]
  %\framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
    % \Require{%
    %   $D$ is the set of alternative recipient devices.
    % }
    \Function{\Recv}{sender}
      \State $\LRV \gets \CreateOnionLayer()$
      \State layers $\gets [\,]$
      % \While{len(layers) $ < l$}
      %   \State layers.append(\CreateOnionLayer())
      % \EndWhile
      % \State \Hrecforward \gets properly encrypted layers
      % \State \Hrecbackward \gets properly encrypted layers
      % \State \Hsendforward \gets sender.\Send(\Hrecforward, \LRV)
      % \State \Hbackward \gets \Hrecbackward || \Hsendbackward
      % \State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
      % \State \Return $H_\rdv$
      %   \Comment{Give to sender out-of-bound.}
    \EndFunction
  \end{algorithmic}
  %\end{minipage}}

@@

  \vspace{0.3em}
  %\framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
    % \Require{%
    %   $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
    %   \(D\) is a set of device addresses.
    %   $\pk_D$ is the public key of device set $D$.
    %   $L$ is the length of the route,
    %   $\theta$ is the threshold of probability of failure.%
    % }
    \Function{\ExtendRoute}{$\mathcal{H}, l$}
      \If{$L\leq 0$}
        \State \Return $H$
      \EndIf
      \State $D\gets \CreateOnionLayer[\theta]$
      \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
      \State \Return $\ExtendRoute[H, L-1, \theta]$
    \EndFunction
  \vspace{0.3em}
    \Function{\CreateOnionLayer}{\null}
      \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
      \State $D\gets \{(d, \pk_d, p_d)\}$
      \While{$\prod_{d\in D} p_d > \theta$}
        \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
        \State $D\gets D\cup \{(d, \pk_d, p_d)\}$
      \EndWhile
      \State \Return $D$
    \EndFunction
  \end{algorithmic}
  %\end{minipage}}
  \caption{\label{fig:route building algo}The route building algorithm}
\end{figure}
